### 2023-03-24 resilience.tex
details

To decide the  bounded resilience problem (BRP), we decide $n \times m$ coverability questions: is state $b_j$ coverable from ideal $J_i$ ? If all these $n \times m$ coverability questions are positive then we compute $K=max(k_a \mid a=1,..,m \times n)$ and we deduce that  $\mathscr{S}$ is $K$-resilient \alain{else $\mathscr{S}$ is not $K$-resilient...et alors qu'en déduit-on ?}. Since coverability is decidable for completion-post-effective $\omega^2$-WSTS, we have shown that both the 
  resilience problem (BRP) and the  
  bounded resilience problem (BRP) are decidable.
\end{proof}

>>>>

To decide the  bounded resilience problem (BRP), we decide $n \times m$ coverability questions: is state $b_j$ coverable from ideal $J_i$ ? If all these $n \times m$ coverability questions are positive then we compute $K=max(k_a \mid a=1,..,m \times n)$ \alain{comment trouver les $k_a$ ?} and we deduce that  $\mathscr{S}$ is $K$-resilient \alain{else $\mathscr{S}$ is not $K$-resilient...et alors qu'en déduit-on ? il pourrait exister un $K' \geq K$ pour lequel $\mathscr{S}$ est K'-resilient....}. Since coverability is decidable for completion-post-effective $\omega^2$-WSTS, we have shown that both the 
  resilience problem (BRP) and the  
  bounded resilience problem (BRP) are decidable.
\end{proof}
